% ── Personal Projects ──────────────────────────────────────────────────────────
\rleftsection{Personal Projects}

\projectentry{\href{https://github.com/raycast/extensions/tree/HEAD/extensions/toothpick/}{Toothpick}}{Raycast Extension}{2022 -- Present}{%
Bluetooth extension for Raycast. Provides shortcuts for quick Bluetooth management. 42.5k+ installs.}

\jobsep
\projectentry{\href{https://github.com/VladCuciureanu/Wren}{Wren}}{CLI Tool}{2025 -- Present}{%
CLI that polls GitHub CI status and plays ambient soundscapes through FFmpeg, mapping build states to layered audio.}

\jobsep
\projectentry{\href{https://github.com/VladCuciureanu/Cora}{Cora}}{Apple Watch Service}{2025 -- Present}{%
Service that receives heart rate data from an Apple Watch and commits each reading to a GitHub repo, turning your contribution graph into a live heartbeat record.}

\jobsep
\projectentry{\href{https://github.com/VladCuciureanu/Reverie}{Reverie}}{GitHub Action}{2025 -- Present}{%
GitHub Action gate that polls a sleep tracker and blocks production deploys while the on-call engineer is asleep.}

\jobsep
\projectentry{\href{https://github.com/VladCuciureanu/Maud}{Maud}}{GitHub Action}{2025 -- Present}{%
GitHub Action that prints a sigh to the workflow log and exits successfully. Does nothing else.}

\jobsep
\projectentry{\href{https://github.com/VladCuciureanu/Eugene}{Eugene}}{CLI Tool}{2025 -- Present}{%
CLI wrapper that intercepts failed commands and walks the user through an interactive five-stage grief dialogue before allowing a retry.}

\jobsep
\projectentry{\href{https://github.com/VladCuciureanu/Nigel}{Nigel}}{CLI Tool}{2025 -- Present}{%
CLI that wraps file deletion in a mock bureaucratic review process with randomized approval, audit logs, and an appeal mechanism.}
