%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Projects}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Contributor}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/withastro/astro}{Astro}} % Project
    {Astro is the web framework for building content-driven websites.} % Description
    {Node} % Technologies
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/AykutSarac/jsoncrack.com}{JSONCrack}} % Project
    {Visualization OSS that transforms various data formats into interactive graphs.} % Description
    {React, Node} % Technologies
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/toeverything/AFFiNE}{AFFiNE}} % Project
    {Open-source alternative to Notion \& Miro.} % Description
    {React, Node} % Technologies
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/code4romania/seismic-risc}{Seismic Risc}} % Project
    {Platform designed for tracking buildings at risk of collapsing in the event of an earthquake.} % Description
    {React, Django} % Technologies
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/code4romania/monitorizare-vot}{Monitorizare Vot}} % Project
    {App built for monitoring polling stations and for reporting noticeable irregularities.} % Description
    {React, .Net Core} % Technologies
    {2020} % Date(s)

%---------------------------------------------------------
\end{cvhonors}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Personal}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/raycast/extensions/tree/HEAD/extensions/toothpick/}{Toothpick}} % Project
    {Bluetooth extension for Raycast. Provides shortcuts for quick Bluetooth management. (42.5k+ Installs)} % Description
    {React, Node} % Technologies
    {2022+} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/VladCuciureanu/Wren}{Wren}} % Project
    {CLI that polls GitHub CI status and plays ambient soundscapes through FFmpeg, mapping build states to layered audio.} % Description
    {TypeScript, Novelty} % Technologies
    {2025} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/VladCuciureanu/Cora}{Cora}} % Project
    {Service that receives heart rate data from an Apple Watch and commits each reading to a GitHub repo, turning your contribution graph into a live heartbeat record.} % Description
    {TypeScript, Novelty} % Technologies
    {2025} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/VladCuciureanu/Eugene}{Eugene}} % Project
    {CLI wrapper that intercepts failed commands and walks the user through an interactive five-stage grief dialogue before allowing a retry.} % Description
    {TypeScript, Novelty} % Technologies
    {2025} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://github.com/VladCuciureanu/Nigel}{Nigel}} % Project
    {CLI that wraps file deletion in a mock bureaucratic review process with randomized approval, audit logs, and an appeal mechanism.} % Description
    {TypeScript, Novelty} % Technologies
    {2025} % Date(s)

%---------------------------------------------------------
\end{cvhonors}
